A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Similarity ref
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1055 43ef1190-90fd-4dd7-a769-d0121f02b80e

In \cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.\todo{discuss SPARQL cache complexity}

@@

Estimating the freshness lifetime is a challenging problem for data
owners. It must necessarily involve the human users involved in the
publishing cycle since they are making a commitment about future
changes. Designing user support systems as well as interfaces that fit
the publisher's workflow, is an important problem.

For SPARQL endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.\todo{more on this difficulty}

>>>>

In \cite{umbrich2012hybrid}, the term caching was used in a different
sense than we do, they rather prefetched an entire dataset to a local
store and based on heuristics tried to determine which parts of the
query should be evaluated remotely and locally. \cite{lampo2011cache}
explored when caching had a positive effect on complex SPARQL
queries.

@@

Estimating the freshness lifetime is a challenging problem for data
owners. It must necessarily involve the human users involved in the
publishing cycle since they are making a commitment about future
changes. Designing user support systems as well as interfaces that fit
the publisher's workflow is an important problem.

For SPARQL endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.

We believe that  \cite{ldf1} and \cite{hogan2014paths} prematurely
reject caching in connection to SPARQL. They are correct that
currently, query results can only be cached on a per-query
basis. Moreover, semantically insignificant changes to a query, such
as whitespace or the order of triple patterns in a basic graph
pattern, currently causes problems for caches. The latter problem can
probably be fixed by developing digest algorithms. Such algorithms
exist, but are focused on cryptographical strength, and much simpler
algorithms could be used for this problem.

Furthermore, by using similarity measures, like those discussed in
